Pulling oral and IV data from CvTdb

### 2023-10-12 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Updated some methods and data

# Harmonize values for easier analysis
sql_query <- sql_query %>%
  mutate(
    species = tolower(species),
    sex = tolower(sex),
    loq = as.numeric(loq),
    n_subjects_in_series = as.numeric(n_subjects_in_series),
    dose_level_normalized = as.numeric(dose_level_normalized),
    dose_level_original = as.numeric(dose_level_original),
    dose_volume_units = str_extract(dose_volume,
                                    pattern = "(?<=[:space:]).+"),
    dose_volume = as.numeric(str_extract(dose_volume,
                                         pattern = "^(\\d|\\.)*")),
    dose_duration_units = str_extract(dose_duration,
                                      pattern = "(?<=[space]).+"),
    dose_duration = as.numeric(str_extract(dose_duration,
                                pattern = "^\\d")),
    radiolabeled = ifelse(radiolabeled == 1, TRUE, FALSE)
  )
sql_query <- sql_query %>%
  rename_with(~gsub(pattern = "fk_", replacement = "",
                         .x), .cols = contains("fk_"))

@@

```{r}
cvt_date <- Sys.Date()
save(cvt_df, file = "data/cvt.rda", compress = "bzip2")
save(cvt_date, file = "data/cvt_download_date.rda")
```

>>>>

# Harmonize values for easier analysis
sql_query <- sql_query %>%
  mutate(
    species = tolower(species),
    sex = tolower(sex),
    loq = as.numeric(loq),
    n_subjects_in_series = as.numeric(n_subjects_in_series),
    dose_level_normalized = as.numeric(dose_level_normalized),
    dose_level_original = as.numeric(dose_level_original),
    dose_volume_units = stringr::str_extract(dose_volume,
                                    pattern = "(?<=[:space:]).+"),
    dose_volume = as.numeric(stringr::str_extract(dose_volume,
                                         pattern = "^(\\d|\\.)*")),
    dose_duration_units = stringr::str_extract(dose_duration,
                                      pattern = "(?<=[space]).+"),
    dose_duration = as.numeric(stringr::str_extract(dose_duration,
                                pattern = "^\\d")),
    radiolabeled = ifelse(radiolabeled == 1, TRUE, FALSE)
  )
sql_query <- sql_query %>%
  dplyr::rename_with(~gsub(pattern = "fk_", replacement = "",
                         .x), .cols = contains("fk_"))

@@

```{r}
cvt_date <- Sys.Date()
cvt <- cvt_df
save(cvt, file = "data/cvt.rda", compress = "bzip2")
save(cvt_date, file = "data/cvt_date.rda")
```
